---
title: "Obesity Project"
output: html_document
---

```{r}
# Import Packages
library(lme4)
library(lmerTest)
library(multcomp)
library(car)
library(nortest)
install.packages("tidyverse")
library(tidyverse)
library(ggplot2)
library(ggpubr)
library(broom)
library(AICcmodavg)
install.packages("ggpubr")
```

```{r}

install.packages("dplyr")
install.packages("multcomp")
library(multcomp)
install.packages("lme4")
library(lme4)
install.packages("lmerTest")
library(lmerTest)
install.packages("car")
library(car)

install.packages("nortest")
library(nortest)
install.packages("sf")
install.packages("agricolae")
library(agricolae)
```

``


```{r}
# Read in Data
obesity_csv <-  read.csv(file = "/Users/12563/Documents/Obesity Project/Obesity.csv")

```



```{r}
head(obesity_csv)
```

```{r}
tail(obesity_csv)
```


```{r}
glimpse(obesity_csv)
```
There are 73 columns or variables in the data set. Furthermore, there are 10,199 observations, rows, or participants that participated in this COPDGene study.

Now, let us check the mean of a few columns of data:

```{r}
# Checking the mean of a few variables
mean(obesity_csv$Height_CM_P1)
```

```{r}
mean(obesity_csv$Age_P1)
```
The average age of our participants is 59.


```{r}
mean(obesity_csv$BMI_P1)
```
The average BMI amung participants is 28.83.


```{r}
mean(obesity_csv$ATS_PackYears_P1, na.rm=TRUE)
```


```{r}
# Looking at the variable names
colnames(obesity_csv)
```



```{r}

# Selecting Vairables of interest
my_data <- as_tibble(obesity_csv)
my_data

my_data %>% select(sid, Age_P1,gender,race,SmokCigNow_P1, finalGold_P1, BMI_P1, Diabetes_P1, HighBloodPres_P1, HighCholest_P1, CoronaryArtery_P1, ATS_PackYears_P1, )

```
The table above is a table of the columns (variables) of intrest in the Obesity Study.



```{r}
summary(obesity_csv$Age_P1)
```


```{r}
summary(obesity_csv$finalGold_P1)
```


Now it is time to create some tables.

```{r}
# Gender Table
tab_gender <- table(obesity_csv$gender,useNA = "always")
tab_gender 
```


```{r}
# Percentage table for Gender Table 
prop.table(tab_gender)
prop.table(tab_gender)*100

```

```{r}
# Gender & Diabetes Table
tab_1 <- table(obesity_csv$gender, obesity_csv$Diabetes_P1)
tab_1
colnames(tab_1)  = c("Non-Diabetic", "Diabetic")
rownames(tab_1) = c("Male", "Female")
```


```{r}
Gender_BMI_mean <- aggregate(BMI_P1 ~ gender, data = obesity_csv, mean)
Gender_BMI_mean
```


```{r}
Gender_BMI_mean <- aggregate(BMI_P1 ~ gender, data = obesity_csv, sd)
Gender_BMI_mean
```

```{r}
tab_2 <- table(obesity_csv$gender, obesity_csv$HighBloodPres_P1)
colnames(tab_2)  = c("No High Blood Pressure", "High Blood Pressure reported")
rownames(tab_2) = c("Male", "Female")
tab_2

```

```{r}
#table command dosent give NA

# GOLD variable table with NA values includes

table_finalgold <- table(obesity_csv$finalGold_P1,useNA = "always")
table_finalgold
```

```{r}
# Percentage table for GOLD variable 
prop.table(table_finalgold)
prop.table(table_finalgold)*100

``` 



```{r}
my_data %>% select(PCAsubtype)
```
```{r}
#PCAsubtype Variable table
table_PCA <- table(obesity_csv$PCAsubtype, useNA = "always")
table_PCA
```

```{r}
# Percentage of PCAsubtype
prop.table(table_PCA)*100
```







#create a mean and standard deviation the PCAsubtype



# create mean and standard deviation of 5 adiposity measures by the PCAsubtype


```{r}

# ABVF Mean
fat_mean_AVBF_PCA <- aggregate(ABVF ~ PCAsubtype, data = obesity_csv, mean)
row.names(fat_mean_AVBF_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_mean_AVBF_PCA
```

```{r}
# AVBF SD
fat_sd_AVBF_PCA <- aggregate(ABVF ~ PCAsubtype, data = obesity_csv, sd)
row.names(fat_sd_AVBF_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_sd_AVBF_PCA
```


```{r}
# SFA Mean
fat_mean_SFA_PCA <- aggregate(SFA ~ PCAsubtype, data = obesity_csv, mean)
row.names(fat_mean_SFA_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_mean_SFA_PCA
```

```{r}
# SFA SD
fat_sd_SFA_PCA <- aggregate(SFA ~ PCAsubtype, data = obesity_csv, sd)
row.names(fat_sd_SFA_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_sd_SFA_PCA
```


```{r}
# PMA Mean
fat_mean_PMA_PCA <- aggregate(PMA ~ PCAsubtype, data = obesity_csv, mean)
row.names(fat_mean_PMA_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_mean_PMA_PCA
```

```{r}
# PMA SD
fat_sd_PMA_PCA <- aggregate(PMA ~ PCAsubtype, data = obesity_csv, sd)
row.names(fat_sd_PMA_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_sd_PMA_PCA
```


```{r}
# PMAlean Mean
fat_mean_PMAlean_PCA <- aggregate(PMAlean ~ PCAsubtype, data = obesity_csv, mean)
row.names(fat_mean_PMAlean_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_mean_PMAlean_PCA
```

```{r}
# PMAlean SD
fat_sd_PMAlean_PCA <- aggregate(PMAlean ~ PCAsubtype, data = obesity_csv, sd)
row.names(fat_sd_PMAlean_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_sd_PMAlean_PCA
```


```{r}
#Liver Density Mean
fat_mean_liverdensity_PCA <- aggregate(Liverdensity ~ PCAsubtype, data = obesity_csv, mean)
row.names(fat_mean_liverdensity_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_mean_liverdensity_PCA
```

```{r}
# Liver Density SD
fat_sd_liverdensity_PCA <- aggregate(Liverdensity ~ PCAsubtype, data = obesity_csv, sd)
row.names(fat_sd_liverdensity_PCA) <- c("Normal", "HR Airway Disease without Emphysema", "HR Airway Disease with Emphysema", "Emphysema without HR Airway Disease")
fat_sd_liverdensity_PCA
```


```{r}

tmpo = subset(obesity_csv, PCAsubtype =='-9')
mean(tmpo$Liverdensity)
```

Result Section 1. Abdomen Visceral Fat (ABVF):


```{r}

# ANOVA tests whether any of the group means are different from the overall mean of the data by checking the variance of each individual group aganist the overall variance of the data. If one or more groups falls outside the range of variation predicted by the null hypothesis (all group means are equal), then the test is statistically significant. 

# the aov() function will calculate the test statistic for ANOVA and determine whether there is significant variation among the groups formed by the levels of the independent variable

#This is a one-way ANOVA, we are modeling the Visceral Fat ABVF as a function of the PCAsubtypes 

#ANOA Test Hypotheses:
#Null hypothesis: the means of the different groups are the same 
#Alternative Hypothesis: At least one sample mean is not equal to the others

# One-Way Anova Table
obesity_csv$PCAsubtype = as.factor(obesity_csv$PCAsubtype)
is.factor(obesity_csv$PCAsubtype)
one.way <- aov(ABVF ~ PCAsubtype, data = obesity_csv)

summary(one.way)
```

The Df column displays the degrees of freedom for the independent variable (the number of levels in the variable minus 1), and the degrees of freedom for the residuals (the total number of observations minus one and minus the number of levels in the independent variables)

The Sum Sq column displays the sum of squares (a.k.a. the total variation between the group means and the overall mean

The Mean Sq column is the mean of the sum of squares, calculated by dividing the sum of squares by the degrees of freedom for each parameter.

The F-value column is the test statistic from the F test. This is the mean square of each independent variable divided by the mean square of the residuals. The larger the F value, the more likely it is that the variation caused by the independent variable is real and not due to chance

The Pr(>F) column is the p-value of the F-statistic. This shows how likely it is that the F-value calculated from the test would have occurred if the null hypothesis of no difference among group means were true

The p-value of the PCAsubtype variable is very small (p < 0.01), so it appears that the PCAsubtype does have a real impact on the Visceral Fat.


```{r}
Tmp = obesity_csv["ABVF", "PCAsubtype"]
Tmp_1 = obesity_csv[ , c(65,63)]
Tmp.cc = Tmp_1[complete.cases(Tmp_1), ]
#Check Assumptions
Tmp_bind_1 = cbind(one.way$residuals, Tmp.cc)



```

```{r}
colnames(Tmp_bind_1)[1]=c('residuals')
```


```{r}
# AVBF Box Plot
p_1 <- ggplot(obesity_csv, aes(x=PCAsubtype, y=ABVF, fill=PCAsubtype)) +
    geom_boxplot(alpha=0.7) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=4, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set1")
plot(p_1)
```

```{r}
# Post-Hoc Analysis
posthoc=glht(one.way,linfct=mcp(PCAsubtype ='Tukey'))
summary(posthoc)
confint(posthoc)
```

```{r}
# Now we will perform the Kruskal-Wallis Test
kruskal.test(ABVF ~ PCAsubtype, data = obesity_csv)
```

```{r}
# Multiple Pairwise-Comparison between groups
# Wilcoxon Rank Sum Test with Continuity Correction
pairwise.wilcox.test(obesity_csv$ABVF, obesity_csv$PCAsubtype,
                 p.adjust.method = "BH")
```




```{r}
Dmatrix.tmp=subset(Tmp_bind_1,Tmp_bind_1[,3]=='-9')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

```
```{r}
# Have to use Kolmogorov-Smirnov Test here because due to data
ks.test(Dmatrix.tmp[,1], "pnorm")
```

# ANOVA conditions are not valid 
# Switch to non-parametric

```{r}
Dmatrix.tmp_2=subset(Tmp_bind_1,Tmp_bind_1[,3]=='1')
#Dmatrix.tmp;dim(Dmatrix.tmp) 

# Checking for Normality 
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_2[,1])
```


```{r}
Dmatrix.tmp_3=subset(Tmp_bind_1,Tmp_bind_1[,3]=='2')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

# Checking for Normality 
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_3[,1])
```


```{r}
Dmatrix.tmp_4=subset(Tmp_bind_1,Tmp_bind_1[,3]=='3')
#Dmatrix.tmp;dim(Dmatrix.tmp)

# Checking for Normality 
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_4[,1])
```

```{r}
levels(obesity_csv$PCAsubtype) <- c("-9 = Normal", "1 = HR Airway Disease without Emphysema", "2 = HR Airway Disease with Emphysema", "3 = Emphysema without HR Airway Disease")

levels(obesity_csv$PCAsubtype)
```

```{r}
levels(obesity_csv$newHRsubtype) <- c("0 = None", "1 = HR Airway with HR Emph", "2 = HR Airway", "3 = HR Emph", "4 = Mod Airway + HR", "5 = Mod Airway Only")
```




```{r}
memory.limit()
memory.limit(24000)

```


```{r}
install.packages("car")
library(car)
```
```{r}
install.packages("reshape2")
library(reshape2)
```

Result Section 2. Subcutaneous Fat Area (SFA):

```{r}
# ANOVA Table
one.way_SFA_PCA <- aov(SFA ~ PCAsubtype, data = obesity_csv)

summary(one.way_SFA_PCA)
```
The p-value of the PCAsubtype variable is very small (p < 0,01), so it appears that the PCAsubtpe does have a real impact on the SFA fat.

```{r}
Tmp = obesity_csv["SFA", "PCAsubtype"]
Tmp_1 = obesity_csv[ , c(71,63)]
Tmp.cc = Tmp_1[complete.cases(Tmp_1), ] 
#Check Assumptions
Tmp_bind = cbind(one.way_SFA_PCA$residuals, Tmp.cc)


```


```{r}
# Box Plot
p_3 <- ggplot(obesity_csv, aes(x=PCAsubtype, y=SFA, fill=PCAsubtype)) +
    geom_boxplot(alpha=0.7) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=4, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set1")

plot(p_3)
```

```{r}
# Post-Hoc Analysis
posthoc=glht(one.way_SFA_PCA,linfct=mcp(PCAsubtype ='Tukey'))
summary(posthoc)
confint(posthoc)
```


```{r}
# Complete Kruskal-Wallis Test

kruskal.test(SFA ~ PCAsubtype, data = obesity_csv)
```

```{r}
# Wilcoxon Rank Sum Test with Continuity Correction
pairwise.wilcox.test(obesity_csv$SFA, obesity_csv$PCAsubtype,
                 p.adjust.method = "BH")
```

```{r}
Dmatrix.tmp=subset(Tmp_bind_1,Tmp_bind_1[,3]=='-9')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

```
```{r}
# Have to use Kolmogorov-Smirnov Test here because due to data
ks.test(Dmatrix.tmp[,1], "pnorm")
```


```{r}
install.packages("nortest")
library(nortest)
```
```{r}
install.packages("onewaytests")
library(onewaytests)
```

```{r}
Dmatrix.tmp_2=subset(Tmp_bind_1,Tmp_bind_1[,3]=='1')
#Dmatrix.tmp;dim(Dmatrix.tmp) 


# Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_2[,1])
```

```{r}
Dmatrix.tmp_3=subset(Tmp_bind_1,Tmp_bind_1[,3]=='2')
#Dmatrix.tmp;dim(Dmatrix.tmp) 


# Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_3[,1])
```

```{r}
Dmatrix.tmp_4=subset(Tmp_bind_1,Tmp_bind_1[,3]=='3')
#Dmatrix.tmp;dim(Dmatrix.tmp) 

# Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_4[,1])
```


Results Section 3. Pectoralis Muscle Area (PMA):



```{r}
# ANOVA Table
obesity_csv$PCAsubtype = as.factor(obesity_csv$PCAsubtype)
is.factor(obesity_csv$PCAsubtype)
one.way_PMA_PCA <- aov(PMA ~ PCAsubtype, data = obesity_csv)

summary(one.way_PMA_PCA)
```

```{r}
# Box Plot
p_5 <- ggplot(obesity_csv, aes(x=PCAsubtype, y=PMA, fill=PCAsubtype)) +
    geom_boxplot(alpha=0.7) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=4, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set1")

plot(p_5)
```
```{r}
# Post-Hoc Analysis
posthoc=glht(one.way_PMA_PCA,linfct=mcp(PCAsubtype ='Tukey'))
summary(posthoc)
confint(posthoc)
```


```{r}
Tmp = obesity_csv["PMA", "PCAsubtype"]
Tmp_1 = obesity_csv[ , c(69,63)]
Tmp.cc = Tmp_1[complete.cases(Tmp_1), ]
#Check Assumptions
Tmp_bind = cbind(one.way_PMA_PCA$residuals, Tmp.cc)


```


```{r}
# Complete Kruskal-Wallis Test

kruskal.test(PMA ~ PCAsubtype, data = obesity_csv)
```

```{r}
# Wilcoxon Rank Sum Test with COntinuity Correction
pairwise.wilcox.test(obesity_csv$PMA, obesity_csv$PCAsubtype,
                 p.adjust.method = "BH")
```



```{r}
Dmatrix.tmp=subset(Tmp_bind_1,Tmp_bind_1[,3]=='-9')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

```
```{r}
# Have to use Kolmogorov-Smirnov Test here because due to data
ks.test(Dmatrix.tmp[,1], "pnorm")
```

```{r}
Dmatrix.tmp_2=subset(Tmp_bind_1,Tmp_bind_1[,3]=='1')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

# Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_2[,1])
```

```{r}
Dmatrix.tmp_3=subset(Tmp_bind_1,Tmp_bind_1[,3]=='2')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

# Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_3[,1])
```

```{r}
Dmatrix.tmp_4=subset(Tmp_bind_1,Tmp_bind_1[,3]=='3')
#Dmatrix.tmp;dim(Dmatrix.tmp)

# Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_4[,1])
```

Results Section 4. Lean Pectoralis Muscle Area (PMAlean):

```{r}
#ANOVA Table
one.way_PMAlean_PCA <- aov(PMAlean ~ PCAsubtype, data = obesity_csv)

summary(one.way_PMAlean_PCA)
```
The p-value of the PCAsubtype variable is very very small (p < 0,01), so it appears that the PCAsubtpe does have a real impact on the PMAlean fat.

```{r}
Tmp = obesity_csv["PMAlean", "PCAsubtype"]
Tmp_1 = obesity_csv[ , c(70,63)]
Tmp.cc = Tmp_1[complete.cases(Tmp_1), ]
#Check Assumptions
Tmp_bind = cbind(one.way_PMAlean_PCA$residuals, Tmp.cc)


```


```{r}
colnames(Tmp_bind)[1]=c('residuals')
```


```{r}
# Box Plot
p_7 <- ggplot(obesity_csv, aes(x=PCAsubtype, y=PMAlean, fill=PCAsubtype)) +
    geom_boxplot(alpha=0.7) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=4, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set1")

plot(p_7)
```

```{r}

# Post-Hoc Analysis
posthoc=glht(one.way_PMAlean_PCA,linfct=mcp(PCAsubtype ='Tukey'))
summary(posthoc)
confint(posthoc)
```

```{r}
# Complete Kruskal-Wallis Test

kruskal.test(PMAlean ~ PCAsubtype, data = obesity_csv)
```


```{r}
# Wilcoxon Rank Sum Test with Continuity Correction

pairwise.wilcox.test(obesity_csv$PMAlean, obesity_csv$PCAsubtype,
                 p.adjust.method = "BH")
```

```{r}
Dmatrix.tmp=subset(Tmp_bind_1,Tmp_bind_1[,3]=='-9')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

```
```{r}
# Have to use Kolmogorov-Smirnov Test here because due to data
ks.test(Dmatrix.tmp[,1], "pnorm")
```

```{r}
Dmatrix.tmp_2=subset(Tmp_bind_1,Tmp_bind_1[,3]=='1')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

#Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_2[,1])
```

```{r}
Dmatrix.tmp_3=subset(Tmp_bind_1,Tmp_bind_1[,3]=='2')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

#Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_3[,1])
```


```{r}
Dmatrix.tmp_4=subset(Tmp_bind_1,Tmp_bind_1[,3]=='3')
#Dmatrix.tmp;dim(Dmatrix.tmp) 

#Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_4[,1])
```

Result Section 5. Liver Density.

```{r}
# ANOVA Table
obesity_csv$PCAsubtype = as.factor(obesity_csv$PCAsubtype)
is.factor(obesity_csv$PCAsubtype)
one.way_Liverdensity_PCA <- aov(Liverdensity ~ PCAsubtype, data = obesity_csv)

summary(one.way_Liverdensity_PCA)
```
The p-value of the PCAsubtype variable is decently high (p > 0.01), so it appears that the PCAsubtype does not have a real impact on the Liverdensity fat.


```{r}
Tmp = obesity_csv["Liverdensity", "PCAsubtype"]
Tmp_1 = obesity_csv[ , c(72,63)]
Tmp.cc = Tmp_1[complete.cases(Tmp_1), ]
#Check Assumptions
Tmp_bind = cbind(one.way_Liverdensity_PCA$residuals, Tmp.cc)


```


```{r}
# Box Plot
p_9 <- ggplot(obesity_csv, aes(x=PCAsubtype, y=Liverdensity, fill=PCAsubtype)) +
    geom_boxplot(alpha=0.7) +
    stat_summary(fun.y=mean, geom="point", shape=20, size=4, color="red", fill="red") +
    theme(legend.position="none") +
    scale_fill_brewer(palette="Set1")

plot(p_9) 
```


```{r}
# Post Hoc Analysis
posthoc=glht(one.way_Liverdensity_PCA,linfct=mcp(PCAsubtype ='Tukey'))
summary(posthoc)
confint(posthoc)
```

```{r}
# Complete Kruskal-Wallis Test

kruskal.test(Liverdensity ~ PCAsubtype, data = obesity_csv)
```

```{r}
# Wilcoxon Rank Sum Test with Continuity Correcrtion
pairwise.wilcox.test(obesity_csv$Liverdensity, obesity_csv$PCAsubtype,
                 p.adjust.method = "BH")
```

```{r}
# Checking for Normality

Dmatrix.tmp=subset(Tmp_bind_1,Tmp_bind_1[,3]=='-9')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

```
```{r}
# Have to use Kolmogorov-Smirnov Test here because due to data
ks.test(Dmatrix.tmp[,1], "pnorm")
```

```{r}
Dmatrix.tmp_2=subset(Tmp_bind_1,Tmp_bind_1[,3]=='1')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

#Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_2[,1])
```

```{r}
Dmatrix.tmp_3=subset(Tmp_bind_1,Tmp_bind_1[,3]=='2')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

#Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_3[,1])
```

```{r}
Dmatrix.tmp_4=subset(Tmp_bind_1,Tmp_bind_1[,3]=='3')
#Dmatrix.tmp;dim(Dmatrix.tmp)  

#Checking for Normality
# Shapiro-Wilk Normality Test
shapiro.test(Dmatrix.tmp_4[,1])
```

# Extra

```{r}
# Perform Dunn Test
install.packages("FSA")
library(FSA)
dunnTest(Liverdensity ~ PCAsubtype, data = obesity_csv, method = "bh")
```

```{r}
# Perform kwALLPairsNemmyiTest
# Performs Nemenyi's non-parametric all-pair comparison test for Kruskal-type ranked data
# Post-Hoc test for non-parametric comparison
#Pairwise Test for multiple comparison of mean Rank Sums (Nemenyi-Tests)
# The outcome of the 
install.packages("PMCMRplus")
library(PMCMRplus)
kw <- kwAllPairsNemenyiTest(Liverdensity ~ PCAsubtype, data = obesity_csv)
```

```{r}
kw <- kwAllPairsNemenyiTest(Liverdensity ~ PCAsubtype, data = obesity_csv)
print(kw)
```


```{r}
obesity_csv$PCAsubtype <- ifelse(obesity_csv$PCAsubtype == -9, "normal", obesity_csv$PCAsubtype)
obesity_csv$PCAsubtype <- ifelse(obesity_csv$PCAsubtype == 1, "HR Airway Disease without Emphysema", obesity_csv$PCAsubtype)
obesity_csv$PCAsubtype <- ifelse(obesity_csv$PCAsubtype == 2, "HR Airway Disease with Emphysema", obesity_csv$PCAsubtype)
obesity_csv$PCAsubtype <- ifelse(obesity_csv$PCAsubtype == 3, "Emphysema without HR Airway Disease", obesity_csv$PCAsubtype)
obesity_csv$PCAsubtype <- as.factor(obesity_csv$PCA)
```





```{r}
levels(obesity_csv$PCAsubtype) <- c("-9 = Normal", "1 = HR Airway Disease without Emphysema", "2 = HR Airway Disease with Emphysema", "3 = Emphysema without HR Airway Disease")

PCA_L <- levels(obesity_csv$PCAsubtype)
```



```{r}
kw_summary <- summary(kw)
```

```{r}
as.character(PCA_L) 
as.factor(PCA_L)
```




